\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles

### 2019-06-21 IPANEMAP-2019.tex

\begin{figure}
	\newcommand{\W}{.725}
	{\centering\begin{tabular}{@{}c@{}c@{}c@{}}
			{\sf {\bfseries A} -- \relsize{-1}Bi-probing MCC \emph{vs} Min MCC of mono-probing}\\
			\includegraphics[width=\W\linewidth,trim=1cm 1cm .8cm .3cm,clip]{graphs/didy/MCC-vs-Min}\\[.5em]
			{\sf {\bfseries B} -- \relsize{-1}Bi-probing MCC \emph{vs} Average MCC of mono-probing}\\
			\includegraphics[width=\W\linewidth,trim=1cm 1cm .8cm .3cm,clip]{graphs/didy/MCC-vs-Avg}\\[.5em]
			{\sf {\bfseries C} -- \relsize{-1}Bi-probing MCC \emph{vs} Max MCC of mono-probing}\\
			\includegraphics[width=\W\linewidth,trim=1cm 1cm .8cm .3cm,clip]{graphs/didy/MCC-vs-Max}\\
		\end{tabular}\\}
	\caption{Shift in \OurTool{} predictive capacity (MCC) observed upon considering two conditions, compared to the worst ({\sf\bfseries A}),  average ({\sf\bfseries B}) 
		and best ({\sf\bfseries C}) 
		predictions achieved for mono-probing conditions. Green and red edges indicate enhanced and degraded predictions respectively compared to the reference (Min% 
		, Max 
		or Average of conditions). Thickness indicates absolute shift value (only values above 5\% reported for readability).\label{fig:pairwise}}
\end{figure}

>>>>

\begin{figure}
	\newcommand{\W}{.86}
	{\centering\includegraphics[width=\W\linewidth]{graphs/didy/pairs-spiders}\\}
	\caption{Shift in \OurTool{} predictive capacity (MCC) observed upon considering two conditions, compared to the worst ({\sf\bfseries A}),  average ({\sf\bfseries B}) 
		and best ({\sf\bfseries C}) 
		predictions achieved for mono-probing conditions. Green and red edges indicate enhanced and degraded predictions respectively compared to the reference (Min% 
		, Max 
		or Average of conditions). Thickness indicates absolute shift value (only values above 5\% reported for readability).\label{fig:pairwise}}
\end{figure}
